---
title: "STA302_proposal"
output: html_notebook
---

Reading in data

```{r}
data_frame <- read.csv("data.csv")
head(data)
data_matrix <- data.matrix(subset(data_frame, select=c(danceability, energy, liveness, mode, tempo, valence)))
head(data_matrix["valance"])
```

```{r}
x1 <- data_matrix[,"danceability"]
x2 <- data_matrix[,"energy"]
x3 <- data_matrix[,"liveness"]
x4 <- data_matrix[,"mode"]
x5 <- data_matrix[,"tempo"]
y <- data_matrix[,"valence"]
x <- data.frame(cbind(x1,x2,x3,x4,x5))
model <- lm(formula = y ~ x1+x2+x3+x4+x5)
y_hat <- predict(model, newdata = x)
e = y - y_hat
rss <- t(e) %*% e
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
